---
output: github_document
editor_options: 
  markdown: 
    wrap: sentence
---

# GlobalFoodPrices

## Overview

**GlobalFoodPrices** is an R package designed to analyze global food expenditure and high food price trends. It provides users with tools to explore food expenditure patterns across countries and assess the prevalence of high food prices over time. The package includes functions for calculating average food expenditure, identifying countries with high food prices, and analyzing expenditure growth. An interactive Shiny app allows users to visualize and engage with the data.

## Key Features

-   **Global Food Expenditure Data**: Access comprehensive data on food expenditure per person across various countries and years.

-   **High Food Price Analysis**: Examine the proportion of countries experiencing high food prices and how these trends change over time.

-   **Interactive Visualization**: Utilize the built-in Shiny app to explore the data interactively, including options to filter by year and country.

-   **Analytical Functions**: Built-in functions for calculating average food expenditure, identifying countries with high food prices, and measuring expenditure growth between years.

## Installation

You can install the development version of `GlobalFoodPrices` directly from GitHub:

```r
# Install GlobalFoodPrices from GitHub
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-PrajaktaChavan0096")
```

## Usage

### 1. Launching the Shiny App
Run the Shiny app to interactively explore global food expenditure and high food price data:

```{r eval=FALSE}
GlobalFoodPrices::launch_shiny_app()
```

### 2. Analyzing Food Expenditure Trends
You can use GlobalFoodPrices functions to calculate average food expenditure and explore trends in high food prices across different countries.

```{r eval=FALSE}

# Example: Calculating Average Food Expenditure for a Specific Year
library(GlobalFoodPrices)
avg_expenditure <- calculate_yearly_avg_expenditure(cleaned_food_expenditure, year = 2020)
print(avg_expenditure)

# Example: Identifying Countries with High Food Prices in a Given Year
high_price_countries <- identify_high_price_countries(cleaned_high_food_prices, year = 2020, threshold = 50)
print(high_price_countries)
```

## Data Sources
Global Food Expenditure Data: Data on annual food expenditure per person across countries.
High Food Price Data: Data indicating the proportion of countries experiencing high food prices over time.

## License
This project is licensed under the MIT License. See the LICENSE file for more details.

## Contributions
Contributions are welcome! Feel free to fork the repository, submit pull requests, or report issues to help improve the package.

## Documentation
For full documentation and tutorials, visit the pkgdown site here: GlobalFoodPrices Documentation


### Key Sections Updated

1. **Overview**: A brief description of the package’s purpose and main features.
2. **Key Features**: Summarizes the main features available in `GlobalFoodPrices`.
3. **Installation**: Instructions to install from GitHub.
4. **Usage Examples**: Demonstrates the main functions and how to use them, including launching the Shiny app and analyzing data.
5. **Data Sources**: Lists the sources of data used in the package.
6. **License** and **Contributions**: Details about the license and how users can contribute.
7. **Documentation**: Links to the package’s documentation site.

After editing `README.Rmd`, use `devtools::build_readme()` to render `README.md` based on `README.Rmd`, so both files stay in sync:

```r
devtools::build_readme()
```
